\cvsection{Courses and workshops}
\begin{cvcourses}
    \cvcourse
        {Neuromatch Academy Deep Learning 2021}
        {}
        {Neuromatch}
        {Online}
        {Jul. 2021}
        {Intensive 3-week course on advanced Deep Learning techniques.}
    \cvcourse
        {Women-led BioData Science Hackaton}
        {}
        {National Center for Biotechnology Information}
        {Bethesda, MD, USA}
        {May 2019}
        {Week-long Hackaton for women in Bioinformatics at the NIH}
    \cvcourse
        {Neurohackademy 2019}
        {}
        {University of Washington}
        {Seattle, WA, USA}
        {Jul. - Aug. 2019}
        {Neuroimaging and Data Science summer school and hackaton.}
    \cvcourse
        {Bayesian Modeling of Brain Imaging Data}
        {Michele Guindani, PhD}
        {Mexican Asociation of Statistics}
        {Ciudad de México, México}
        {Sep. 2017}
        {Two-day intro course about Bayesian methods in fMRI analysis}
     \cvcourse
         {Basic Course of Applied Neuroscience}
         {}
         {Autonomous University of Baja California}
         {Mexicali, BC, México}
         {Aug. 2016}
         {Two-week course of diverse neuroscience themes
         for psychology students and recent graduates}
    \cvcourse
        {International Course of Neuropsychological Evaluation}
        {Juan-Carlos Arango, PhD}
        {Sinapsis}
        {Mexicali, BC, México}
        {Oct. 2015}
        {Bases of application and evaluation of
            neuropsychological testing in cultures and langagues other
            than those in North America and Western Europe}
\end{cvcourses}

