\vspace{-3.2mm}
\cvsection{Experience}
\vspace{-1.5mm}
\cvsubsection{Research}
\begin{cventries}
    \cventry
        {PhD candidate}
        {Neuroimaging \& Surgical Technologies (NIST) Lab}
        {Montreal, QC, Canada}
        {Aug. 2020 - PRESENT}
        {
            \begin{cvitems}
                \item {Working on developing and improving MRI tools that can
                  improve prediction of progression to Alzheimer's disease.}
                \item {Developed a Quality Control application that heavily improved the efficiency of our QC processes.}
            \end{cvitems}
        }
    \cventry
        {Production Editor}
        {McGill Journal of Medicine}
        {Montreal, QC, Canada}
        {May. 2022 - July. 2024}
        {
            \begin{cvitems}
                \item {Manager of a team of production associates for the
                    preparation of the articles' PDF and HTML galleys for
                    their online publication.}
            \end{cvitems}
        }
    \cventry
        {Master's student researcher}
        {Laboratorio Nacional de Imagen por Resonancia Magnética (LANIREM)}
        {Querétaro, Qro, México}
        {Jul. 2019 - Jan. 2020}
        {
            \begin{cvitems}
                \item {Continued my research work at the new location of the lab.}
                \item {I implemented a Machine Learning Algorithm to classify
                  cocaine-dependence using global metrics of topology from fMRI
                  (Graph Theory Analysis).}
            \end{cvitems}
        }
    \cventry
        {Volunteer research visitor}
        {Laboratory of Neuroimaging, National Institute of Alcohol Abuse and
        Alcoholism (NIAAA)}
        {Bethesda, MD, USA}
        {Mar. - May. 2019}
        {
            \begin{cvitems}
                \item {Got trained on the technique Functional Connectivity
                  Density Mapping (FCDM) developed by Dr. Tomasi
                  to be implemented in the ADDIMEX project.}
                \item {I presented my work on the intramural seminar of the
                  NIAAA and NIDA at the NIH.}
            \end{cvitems}
        }
    \cventry
        {Master's student researcher}
        {Instituto Nacional de Psiquiatría ``Ramón de la Fuente Muñiz''
        (INPRFM)}
        {Ciudad de México, México}
        {Aug. 2017 - June. 2019}
        {
            \begin{cvitems}
                \item {I collaborated in the
                  \href{https://clinicaltrials.gov/ct2/show/study/NCT02986438?term=Jorge+Gonzalez-Olvera&cntry=MX&rank=2}
                {\textit{randomized clinical trial of rTMS in Cocaine Use Disorder}}
                under the supervision of Eduardo Garza, PhD.}
                \item {rTMS administration; Database
                    management; MRI data acquisition, preprocessing, and
                    analysis.}
            \end{cvitems}
        }
    \cventry
        {Research Coordinator}
        {Yaaj México, A.C.}
        {Ciudad de México, México}
        {Mar. 2017 - Jul. 2019}
        {
            \begin{cvitems}
                \item {I coordinated a project in collaboration with United
                    Nations Office on Drugs and Crime (UNODC) to write a guide
                    for Mental Health professionals against
                    \textit{Sexual Orientation and Gender Identity Change Efforts}:
                    \href{https://www.unodc.org/documents/mexicoandcentralamerica/2019/GUIAECOSIGFINAL-compressed.pdf}{\textit{``Nada que curar''}.}}
                \item {I was in charge of science dissemination in the themes
                  of sexual health and sex and gender diversity in youth
                  populations.}
            \end{cvitems}
        }
     \cventry
        {Research intern}
        {Colegio de la Frontera Norte (COLEF)}
        {Tijuana, BC, México}
        {Feb. - Sep. 2015}
        {
            \begin{cvitems}
                \item {I was an intern on the research project:
                    \href{https://estudiosdemograficosyurbanos.colmex.mx/index.php/edu/article/view/1791/pdf}{Mexican parents’ attitudes toward gender equality in family roles and leadership.}}
                  \item {Questionnaire administration to middle school parents
                    and data capturing.}
            \end{cvitems}
        }
\end{cventries}
\vspace{-3mm}
\cvsubsection{Clinical}
\begin{cventries}
    \cventry
        {Psychometrist}
        {Interpsique}
        {Tijuana, BC, México}
        {Jan. 2016 - Mar.2017}
        {
            \begin{cvitems}
                \item {Clinical psychological evaluation (Test administration,
                    scoring and supervised interpretation) under the guidance
                    of a licensed Psychologist.}
            \end{cvitems}
        }
    \cventry
        {Psychology Intern}
        {Hospital de Salud Mental de Tijuana (HSMT)}
        {Tijuana, BC, México}
        {Dec. 2014 - Mar. 2015}
        {
            \begin{cvitems}
                \item {240 supervised clinical hours at the Inpatient
                    Psychiatric Care Unit:
                    Occupational and group therapy, and clinical evaluations.}
            \end{cvitems}
        }
\end{cventries}
 \cvsubsection{Volunteering}
 \begin{cventries}
     \cventry
         {Consultant}
         {COPRED (Council to prevent and eliminate discrimination of Mexico city)}
         {Ciudad de México, México}
         {Apr. 2017 - Jul. 2019}
         {
             \begin{cvitems}
                 \item {Offered expert consultation for the new policies and guidelines
                   related to discrimination matters in the city.}
                 \item {Member of the committee in charge of selection of the
                     new President of the Council.}
             \end{cvitems}
         }
     \cventry
         {Volunteer}
         {CAIPT (Integral Attention Center for Transgender People)}
         {Tijuana, BC, México}
         {Jan. 2017 - Jul. 2017}
         {
             \begin{cvitems}
                 \item {Designed and implemented workshops for the transgender
                   women community of Baja California.}
             \end{cvitems}
         }
 \end{cventries}
